%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% A clean template for an academic CV
%
% Uses tabularx to create two column entries (date and job/edu/citation).
% Defines commands to make adding entries simpler.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[10pt, a4paper]{article}

% Full Unicode support for non-ASCII characters
\usepackage[utf8]{inputenc}

% Useful aliases
\newcommand{\GS}{Goldman Sachs, Banglore, India}
\newcommand{\IITBBS}{Indian Institute of Techonology (IIT), Bhubaneswar}
\newcommand{\MPISWS}{Max Planck Institute for Software Systems (MPI-SWS), Germany}
\newcommand{\SES}{School of Electrical Sciences}
\newcommand{\DSSRG}{Distributed and Smart Systems Research Group}
\newcommand{\IR}{Institute Rank}
\newcommand{\IITH}{Indian Institute of Techonology (IIT), Hyderabad}


% Identifying information
\newcommand{\Title}{Curriculum Vit\ae}
\newcommand{\FirstName}{Madhav}
\newcommand{\LastName}{Tummala}
\newcommand{\Initials}{M}
\newcommand{\MyName}{\FirstName\ \LastName}
\newcommand{\Me}{\textbf{\Initials\ \LastName}}  % For citations
\newcommand{\Email}{madhavtummala@icloud.com}
\newcommand{\PersonalWebsite}{madhavtummala.github.io}
\newcommand{\LabWebsite}{https://sites.google.com/iitbbs.ac.in/dssrg}
\newcommand{\ORCID}{0000-0002-6620-4706}
\newcommand{\POS}{Analyst, Global Markets Compliance}
\newcommand{\Affiliation}{\POS \\ \GS}

% Names for citing coauthors
\newcommand{\SSaha}{S Saha}
\newcommand{\SBharadwaj}{S Bharadwaj}

% Template configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Disable hyphenation
\usepackage[none]{hyphenat}

% Control the font size
\usepackage{anyfontsize}

% Icon fonts (requires using xelatex or luatex)
\usepackage[fixed]{fontawesome5}
\usepackage{academicons}

% Template variables for styling
\newcommand{\TablePad}{\vspace{-0.4cm}}
\newcommand{\SoftwareTitle}[1]{{\bfseries #1}}
\newcommand{\TableTitle}[1]{{\fontsize{11pt}{0}\selectfont \itshape #1}}

% For fancy and multipage tables
\usepackage{tabularx}
\usepackage{multirow}
\usepackage{ltablex}

% Define a new environment to place all CV entries in a 2-column table.
% Left column are the dates, right column the entries.
\usepackage{environ}
\NewEnviron{EntriesTable}{
\TablePad
\begin{tabularx}{\textwidth}{@{}p{0.12\textwidth}@{\hspace{0.02\textwidth}}p{0.86\textwidth}@{}}
  \BODY
\end{tabularx}
}

% Macros to add links and mark publications
\newcommand{\DOI}[1]{doi:\href{https://doi.org/#1}{#1}}
\newcommand{\DOILink}[1]{\href{https://doi.org/#1}{doi.org/#1}}
\newcommand{\Preprint}[1]{\newline • Preprint: \faFilePdf\ \DOILink{#1}}
\newcommand{\Youtube}[1]{\newline • Recording: \faYoutube\, \href{https://www.youtube.com/watch?v=#1}{youtube.com/watch?v=#1}}
\newcommand{\GitHub}[1]{\newline • Code: \faGithub\ \href{https://github.com/#1}{#1}}
\newcommand{\Role}[1]{\newline • Role: #1}
\newcommand{\Website}[1]{\newline • Website: \href{https://#1}{#1}}
\newcommand{\Slides}[1]{\newline • Slides: \faTv\ \href{https://#1}{#1}}
\newcommand{\SlidesDOI}[1]{\newline • Slides: \faTv\ \DOILink{#1}}
\newcommand{\PosterDOI}[1]{\newline • Poster: \faImage\ \DOILink{#1}}
\newcommand{\OA}{\aiOpenAccess\enspace}
\newcommand{\Invited}{\newline • \textbf{Invited talk}}

% Macros to set the year and duration on the left column
\newcommand{\Duration}[1]{\fontsize{10pt}{0}\selectfont #1}
\newcommand{\Year}[1]{\fontsize{10pt}{0}\selectfont #1}
\newcommand{\Ongoing}{present}
%\newcommand{\Ongoing}{$\ast$}
\newcommand{\Future}{future}
\newcommand{\Review}{in review}
\newcommand{\Accepted}{accepted}
\newcommand{\Appointment}[2]{\textbf{#1} \newline #2}

% Define command to insert month name and year as date
\usepackage{datetime}
\newdateformat{monthyear}{\monthname[\THEMONTH], \THEYEAR}

% Set the page margins
\usepackage[a4paper,margin=1.5cm,includehead,headsep=5mm]{geometry}

% To get the total page numbers (\pageref{LastPage})
\usepackage{lastpage}

% No indentation
\setlength\parindent{0cm}

% Increase the line spacing
\renewcommand{\baselinestretch}{1.1}
% and the spacing between rows in tables
\renewcommand{\arraystretch}{1.5}

% Remove space between items in itemize and enumerate
\usepackage{enumitem}
\setlist{nosep}

% Use custom colors
\usepackage[usenames,dvipsnames]{xcolor}

% Set fonts. Requires compilation with xelatex
\usepackage{fontspec}  % required to make older xelatex compile with UTF8

% Configure the font style for sections
\usepackage{sectsty}
\sectionfont{\vspace{0.5cm}\bfseries\fontsize{11pt}{0}\selectfont\uppercase}
\subsectionfont{\vspace{0.2cm}\mdseries\fontsize{11pt}{0}\selectfont\uppercase}

% Set the spacing for sections
%\usepackage{titlesec}
%\titlespacing{\section}{0pt}{0cm}{0.3cm}
%\titlespacing{\subsection}{0pt}{0.3cm}{0.3cm}

% Disable number of sections. Use this instead of "section*" so that the sections still
% appear as PDF bookmarks. Otherwise, would have to add the table of contents entries
% manually.
\makeatletter
\renewcommand{\@seccntformat}[1]{}
\makeatother

% Set fancy headers
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\chead{
  \fontsize{10pt}{11pt}\selectfont
  \MyName
  \hspace{0.2cm} -- \hspace{0.2cm}
  \Title
  \hspace{0.2cm} -- \hspace{0.2cm}
  \monthyear\today
}
\rhead{\fontsize{10pt}{0}\selectfont \thepage/\pageref*{LastPage}}
\renewcommand{\headrulewidth}{0pt}

% Metadata for the PDF output and control of hyperlinks
\usepackage[colorlinks=true]{hyperref}
\hypersetup{
  pdftitle={\MyName\ - \Title},
  pdfauthor={\MyName},
  linkcolor=blue,
  citecolor=blue,
  filecolor=black,
  urlcolor=MidnightBlue
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

% No header for the first page
\thispagestyle{empty}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% HEADER
{\fontsize{22pt}{0}\selectfont\MyName}\\[-0.1cm]
\rule{\textwidth}{0.2pt}
\begin{minipage}[t]{0.595\textwidth}
  \Affiliation
\end{minipage}
\begin{minipage}[t]{0.405\textwidth}
  \begin{flushright}
    Email: \href{mailto:\Email}{\Email}
    \\
    Website: \href{https://\PersonalWebsite}{\PersonalWebsite}
  \end{flushright}
\end{minipage}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education}

\begin{EntriesTable}
  \Duration{2016 -- 2020}  &
  \Appointment{B.Tech in Computer Science}
	{Graduated with Honors with \textbf{CGPA - 9.72/10, \IR  - 2}}
  \newline
	{\SES}
  \newline
	{\IITBBS}
\end{EntriesTable}

\vspace*{-.2\baselineskip}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experience}

\begin{EntriesTable}
  \Duration{2020 -- 2021}  &
  \Appointment{Analyst, \GS}
	{Developing pipelines to analyze, interpret and extract information from Big Data, using MapReduce paradigm among others for Global Markets Compliance}
  \\
  \Duration{2019 -- 2020}  &
  \Appointment{Undergrad Research, \href{https://sites.google.com/iitbbs.ac.in/dssrg}{\DSSRG}}
	{Worked with Dr.Sudipta Saha on Efficient data-sharing in large scale decentralised systems. Resulted in 2 publications and Bachelor's Thesis.}
  \\
  \Duration{Summer, 2019}  &
  \Appointment{Research Intern, \MPISWS}
	{Worked with Dr.Antoine Kaufmann in the Operating System group. Worked on measuring Linux booting process with the aim of optimising microVMs for serverless technologies.}
  % Developed scripts for detailed analysis and measurement of Linux booting process with the aim of optimising microVMs for server-less cloud technologies like AWS Lambda.}
  \\
  \Duration{Summer, 2018}  &
  \Appointment{Research Intern, \IITH}
	{Worked with IITH Compilers Team. Main contributer to \href{https://github.com/IITH-Compilers/Whippersnapper-2.0}{Whippersnapper 2.0}, a synthetic benchmark for P4-16 compilers. Worked on analysing compiler optimisations in LLVM.}
\end{EntriesTable}

\vspace*{-.2\baselineskip}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Publications}

\begin{EntriesTable}
\Year{*}  &
  \Me, \SSaha, \SBharadwaj.
	FlexiCast: Fast Data Sharing in Skewed Wireless Sensor Networks, \emph{IEEE Transactions on Green Communications and Networking}.
  \textit{Under Review}
\\
\Year{*}  &
  \Me, \SSaha.
  MiniCast: Fast and Energy Efficient Many-to-Many Data Sharing for Wireless Networks, \emph{Elsevier Internet of Things Journal}.
  \textit{Under Review}
\\
\Year{2020}  &
  \Me, \SSaha.
  Concurrent Transmission Based Data Sharing with Run-Time Variation of TDMA Schedule, \emph{2020 IEEE 45th Conference on Local Computer Networks (LCN), Sydney, Australia, 2020}.
  \DOI{10.1109/LCN48667.2020.9314855}
  \\
\end{EntriesTable}

\vspace*{-.2\baselineskip}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Awards \& Honors}

\begin{EntriesTable}
  \Year{2020}  &
  Tejaswi Memorial Award for \textbf{Best Bachelors Thesis}, \SES
  \\
  \Year{2019}  &
  Received \textbf{Silver Medal} at Schlumberger’s Coding Hackathon, Inter-IIT Tech Meet
  \\
  \Year{2019}  &
  Team Received \textbf{INR 1 lakh (\~\$1400)} for winning Smart India Hackathon (SIH)
  \\
  \Year{2019} &
  Recieved \textbf{fellowship} from MPI-SWS for working on a summer project.
  \\
  \Year{2019} \& \Year{2017}  &
  Selected for \textbf{ACM International Collegiate Programming Contest (ICPC)} India Regionals.
  \\
  \Year{2017} &
  Changed Major to Computer Science, by securing \textbf{Insititute Rank 1} in the first year.
  \\
\end{EntriesTable}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Presentations}

\begin{EntriesTable}
\Year{2020}  &
  \Me.
  Concurrent Transmission Based Data Sharing with Run-Time Variation of TDMA Schedule.
  \newline
  Presented the paper at IEEE LCN 2020, Sydney, Australia \textit{(Virtual Conference)}
  \\
\Year{2018}  &
  \Me.
  Trapezoidal Decomposition Algorithm and its Applications
  \newline
  Presented as a part of Project Seminar (CS2S001) course at \SES.
\end{EntriesTable}

\vspace*{-.2\baselineskip}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Extracurricular Activities}

\begin{EntriesTable}
  \Duration{2018-2020}  &
  Core Team Member at Google Developer Student Clubs (GDSC).
  Lead workshops on Git/Github for the team and lead several open source projects at the club.
  \GitHub{dsciitbbs}
  \\
  \Duration{2017-2020} &
  Core Head at Robotics and Intelligent Systems Club (RISC).
  Lead several workshops and projects on Aurduino, Raspberry Pi and Python. Represented IIT Bhubaneswar at Tech Expo, Inter-IIT Tech Meet for two consecutive years.
  \GitHub{RISC-IITBBS}
  \\
  \Duration{2017-2020} &
  Lead the Web \& Design team at \href{http://www.e-summit-iitbbs.com}{E-Summit, IIT Bhubaneswar}. Took several workshops on video editing and web development. Apart from leading the website development, created the registration system and promotional videos
  for the event.
  \GitHub{webd-iitbbs}
\end{EntriesTable}

\vspace*{-.2\baselineskip}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Increase the line spacing
\renewcommand{\baselinestretch}{1.1}
% and the spacing between rows in tables
\renewcommand{\arraystretch}{1.2}

\section{Skills}
\TablePad
\begin{tabularx}{\textwidth}{@{}p{0.15\textwidth} p{0.85\textwidth}@{}}
Languages & C, C++, Java, Python, Bash, PHP \\
VCS & Git, SVN \\
DevOps & Docker, K8s, Gitlab \\
% Online courses & Machine Learning by Andrew NG (coursera), Programming with Go by Ian Harris (cousera), Introduction to Kubernetes (edx) \\ 
OS & Unix, macOS, Windows \\
Tools & Apache Hadoop, Apache Spark, Cooja Simulator, Logisim, Matlab, Adobe AE, Adobe PR, Adobe PS, Qt, MS Office \\
\end{tabularx}

\vspace*{-.2\baselineskip}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Languages}
Telugu (Native), English (Fluent), Hindi (Intermediate), Spanish (Basic)

\vspace*{-.2\baselineskip}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{References}
% \TablePad
% \newcommand{\minitab}[2][l]{\begin{tabular}{#1}#2\end{tabular}}
% \begin{tabularx}{\textwidth}{@{}p{0.5\textwidth}p{0.5\textwidth}@{}}
% {\minitab{\textbf{Sudipta Saha}\\ sudipta@iitbbs.ac.in}}
% {\minitab{\textbf{Antoine Kaufmann}\\ antoinek@mpi-sws.org}}  \\ 
% \end{tabularx}
\begin{minipage}[t]{0.5\textwidth}
  \textbf{Sudipta Saha} \\
  sudipta@iitbbs.ac.in \\
  Assistant Professor \\
  Indian Institute of Technology (IIT), Bhubaneswar \\
\end{minipage}
\begin{minipage}[t]{0.5\textwidth}
  \textbf{Antoine Kaufmann} \\
  antoinek@mpi-sws.org \\
  Faculty (tenure-track)\\ 
  Max Planck Institute for Software Systems, Saarbrücken, Germany \\
\end{minipage}
\vspace*{\baselineskip}
\vspace*{\baselineskip}
\begin{minipage}[t]{0.5\textwidth}
  \textbf{Joy Chandra Mukherjee} \\
  joy@iitbbs.ac.in \\
  Assistant Professor \\
  Indian Institute of Technology (IIT), Bhubaneswar \\
\end{minipage}
\begin{minipage}[t]{0.5\textwidth}
  \textbf{Srinivas Pinisetty} \\
  spinisetty@iitbbs.ac.in \\
  Assistant Professor\\ 
  Indian Institute of Technology (IIT), Bhubaneswar \\
\end{minipage}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vfill
\textit{Last updated: \monthyear\today}


\end{document}